Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-08-03 paper/paper.Rmd
move library calls to earlier code chunk (because of changed subsubsubsection order)

```{r setup-2, echo=FALSE, purl=T}
# for knitr spin later
knitr::opts_chunk$set(fig.path = "./paper/figs/",
  cache = T,
  cache.lazy = TRUE)
```

@@

```{r disc, fig.cap="Visualization of 'Leave-one-disc-out' method.", out.width="40%"}
resampling_disc = rsmp("spcv_disc", folds = 5, radius = 300L, buffer = 400L)
resampling_disc$instantiate(task)

@@

```{r buffer, fig.cap="Visualization of the 'Spatial buffering' method from package `blockCV`.", out.width="40%", fig.pos="ht"}
library("mlr3")
library("mlr3spatiotempcv")
task = tsk("ecuador")
resampling_buffer = rsmp("spcv_buffer", theRange = 1000)
resampling_buffer$instantiate(task)

>>>>

```{r setup-2, echo=FALSE, purl=T}
# for knitr spin later
knitr::opts_chunk$set(fig.path = "./paper/figs/",
  cache = FALSE,
  cache.lazy = TRUE)
```

@@

```{r disc, fig.cap="Visualization of 'Leave-one-disc-out' method.", out.width="40%"}
library("mlr3")
library("mlr3spatiotempcv")
task = tsk("ecuador")
resampling_disc = rsmp("spcv_disc", folds = 5, radius = 300L, buffer = 400L)
resampling_disc$instantiate(task)

@@

```{r buffer, fig.cap="Visualization of the 'Spatial buffering' method from package `blockCV`.", out.width="40%", fig.pos="ht"}
resampling_buffer = rsmp("spcv_buffer", theRange = 1000)
resampling_buffer$instantiate(task)
